Twists of supersymmetric gauge theories

### 2019-07-16 paper.tex
adding technical lemmas

\begin{dfn}
A {\bf free classical field theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
\d \colon \cE \to \cE [1] 
\]
such that $(1)$: $\d^2 = 0$ and $(2)$: the pair $(\cE , \d)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to {\rm Dens}_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega\<e_0, \d e_1\> = (-1)^{|e_0|} \int_M \omega(\d e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{dfn}

@@

\begin{dfn}
A {\bf classical field theory} is a free classical field theory $(E, \d, \omega)$ equipped with an even functional
\[
I \in \oloc^+(E)
\]
of cohomological degree zero satisfying the classical master equation 
\[
\d I + \frac{1}{2} \{I,I\} = 0 .
\]
\end{dfn}

Given a classical field theory $(E, \d, \omega, I)$ we denote by
\[S_{BV} = \frac{1}{2} \int_M \omega(e, \d e) + I\in \oloc(E)\]
the BV action of the theory.

\begin{remark}
We will also consider $\ZZ/2$-graded classical field theories which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $\d$ is simply an odd operator.
\end{remark}

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
The classical master equation implies that the operator $\d + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
\[
\left(\cO(E), \d + \{I,-\}\right) .
\]
We will refer to this as the {\bf classical BV complex} of the theory.

\begin{dfn}
A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F\colon (E, \d, \omega, I) \to (E', \d', \omega', I')$ is a linear map of vector bundles
\[
F\colon E \to E'
\]
that intertwines the differentials $\d, \d'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
\end{dfn}

Note that a map of classical field theories induces a map of BV complexes
\[
F^*\colon \left(\cO (\cE)[-1], \d + \{I,-\} \right) \to \left(\cO (\cE')[-1], \d' + \{I',-\} \right) .
\]
This allows us to make the following definition of an equivalence between classical theories.

\begin{dfn} \label{equivalence_def}
A morphism of classical field theories $F\colon (E, \d, \omega, I) \to (E', \d', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
\[
F^* \colon  \left(\cO(\cE')[-1], \d' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], \d + \{I,-\} \right) .
\]
\end{dfn}

\begin{dfn}
Let $(E, \d,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, \d,\omega, I)$ is a map of super dg Lie algebras
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
\]
\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
\end{dfn}

@@

@@

@@

@@

@@

>>>>

\begin{dfn}
A {\bf free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to {\rm Dens}_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{dfn}

@@

\begin{dfn}
A {\bf classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
\[
I \in \oloc^+(E)
\]
of cohomological degree zero satisfying the classical master equation 
\[
Q I + \frac{1}{2} \{I,I\} = 0 .
\]
\end{dfn}

Given a classical field theory $(E, Q, \omega, I)$ we denote by
\[S = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
the BV action of the theory.

\begin{remark}
We will also consider $\ZZ/2$-graded classical field theories which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
\end{remark}

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
\[
\left(\cO(E), Q + \{I,-\}\right) .
\]
We will refer to this as the {\bf classical BV complex} of the theory.

\begin{dfn}
A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is a linear map of vector bundles
\[
F\colon E \to E'
\]
that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
\end{dfn}

Note that a map of classical field theories induces a map of BV complexes
\[
F^*\colon \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
\]
This allows us to make the following definition of an equivalence between classical theories.

\begin{dfn} \label{equivalence_def}
A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
\[
F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
\]
\end{dfn}

\begin{dfn}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
\end{dfn}

@@

\subsection{The classical factorization algebra}

@@

Let $(E, Q, \omega, I)$ be a classical field theory and suppose $\psi_0 \in \sE$ is a fixed solution to the equations of motion. 
Then, we recall the formalism of \cite{CG1,CG2} which extracts a factorization algebra on spacetime that should be thought of as  functions on the formal neighborhood of the derived critical locus of the action $S$ near $\psi_0$.

\begin{dfn}
Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra
\[
\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
\]
\end{dfn}

\subsection{From BRST to BV}

@@

%\begin{dfn}
%A {\bf classical BRST theory} is a finite rank $\ZZ \times \ZZ / 2$-graded vector bundle $F \to M$ equipped with an even differential operator of cohomological degree $+1$
%\[
%Q : \cF \to \cF[1]
%\]
%such that $Q

@@

\def\CVS{{\rm CVS}}
\def\DVS{{\rm DVS}}

@@

\subsection{Notations and conventions}

\begin{dfn}
Let $M$ be a manifold and $E$ a (graded) vector bundle on $M$.  
For any open set $U \subset M$, define the following notations:
\begin{itemize}
\item $\cE(U)$ denotes the graded vector space of smooth sections supported on $U$;
\item $\cE_c(U)$ denotes the graded vector space of compactly supported smooth sections on $U$;
\item $\Bar{\cE}(U)$ denotes the graded vector space of distributional smooth sections on $U$;
\item $\Bar{\cE}_c(U)$ denotes the graded vector space of compactly supported distributional smooth sections on $U$.
\end{itemize}
\end{dfn}

If $E$ is a vector bundle, let $E^!$ denote the ``Verdier dual" vector bundle defined by $E^* \otimes {\rm Dens}_M$, where $E^*$ is the usual linear dual vector bundle. 
For an open set $U \subset M$ let 
\[
\cE(U)^\vee = \Bar{\cE}^!_c(U)
\]
be the continuous, or distributional dual, to $\sE(U)$.

\begin{prop}
Let $E,F$ be vector bundles on $M,N$ respectively.
Then
\[
\cE(M) \Hat{\otimes}_\beta \cF(N) \cong \Gamma(M \times N, E \boxtimes F)
\]
\end{prop}

\begin{dfn}
Let $E$ be a vector bundle on $M$ and $U \subset M$.
The completed algebra of functions on $\cE(U)$ is
\[
\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
\]
\end{dfn}

\subsection{Homological algebra}

There is a functor
\[
dif_c : \CVS \to \DVS .
\]

\begin{dfn}
Suppose $V,W$ are cochain complexes in convenient vector spaces. 
A cochain map $f : V \to W$ is a {\bf quasi-isomorphism} if the map
\[
dif_c (f) : dif_c(V) \to dif_c(W)
\]
is a quasi-isomorphism of differentiable vector spaces.
\end{dfn}

\begin{dfn}
A {\bf filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
\[
\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
\]
where each map is a monomorphism in each cohomological degree. 
A filtered differentiable cochain complex is {\bf complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
\end{dfn}

\begin{thm}[Eilenberg-Moore Comparison]
Let $f : V \to W$ be a map of filtered cochain complexes in an AB4 abelian category.
Suppose, for each integer $n$ there exists an integer $p$ such that $F_p V^n = 0 = F_p W^n$.
If there is an integer $r \geq 0$ such that the induced map on the $r$th page of the corresponding spectral sequences 
\[
f_r^{pq} :  E_r^{pq} V \to E_r^{pq} W
\]
is an isomorphism for all $p,q$, then $f : V \to W$ is a quasi-isomorphism. 
\end{thm}

The category of differentiable vector space is an AB4 category, in fact, it is actually a Grothendieck abelian category.

\begin{thm}[Theorem 2.2.1 of \cite{CG1}]
The category $\DVS$ is a Grothendieck abelian category.
\end{thm}

In particular, we can freely apply the Eilenberg-Moore comparison result to the types of topological cochain complexes we come across in the BV formalism.

\begin{dfn}
A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
\[
\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
\]
where each map is a monomorphism in each cohomological degree and such that the canonical maps $V \to V / F_n V$ induce a quasi-isomorphism $V \to \lim V / F_n V$. 
\end{dfn}
